\bigskip
\bigskip

\cvsection{Education}

\begin{itemize}
    \item Systems Analysis and Development \newline High-Education | FATEC (2016 -- 2019)
    \item Computer Network \newline Full-Certified | ETEC (2016 -- 2017)
    \item Industrial Automation \newline Full-Certified | ITJ (2013 -- 2015)
\end{itemize}

\bigskip
\bigskip

\cvsection{Certifications and Books}

\begin{itemize}
    \item AWS Certified Solutions Architect - AWS.
    \item AWS Certified Cloud Practitioner - AWS.
    \item GitHub Actions - GitHub.
    \item GitLab Certified Associate - Gitlab Inc.
    \item Python Formation Certified - Alura.
    \item Kubernetes: Up and Running - Book.
    \item Fluent Python - Book.
    \item Python Cookbook - Book.
    \item The Hitchhiker's Guide to Python - Book.
    \item Shell Programming (Julio Neves) - Book.
\end{itemize}

\bigskip
\bigskip

\cvsection{Skills}

\begin{itemize}
    \item Soft Skills
\end{itemize}

% \cvtag{Self-Motivated}
\cvtag{Ownership}
\cvtag{Accountability}
% \cvtag{Resilience}
% \cvtag{Attention to Detail}

\divider

\begin{itemize}
    \item Programming
\end{itemize}

\cvtag{Python}
\cvtag{Bash}
\cvtag{Go}
\cvtag{Java}

\divider

\begin{itemize}
    \item Kubernetes Tooling
\end{itemize}

\cvtag{Helm}
\cvtag{ESO}
\cvtag{Kong}
\cvtag{Cert-Manager}
\cvtag{Blackbox}
\cvtag{Prometheus Operator}

\divider

\begin{itemize}
    \item Observability
\end{itemize}

\cvtag{OpenSearch}
\cvtag{ELK Stack}
\cvtag{Fluentbit}
\cvtag{Grafana}
\cvtag{Prometheus}
\cvtag{Zabbix}

\divider

\begin{itemize}
    \item CI/CD and GitOps
\end{itemize}

\cvtag{GitLab}
\cvtag{Github Actions}
\cvtag{ArgoCD}

\divider

\begin{itemize}
    \item Infrastructure as a Code
\end{itemize}

\cvtag{Ansible}
\cvtag{Terraform}

\divider

\begin{itemize}
    \item AWS services
\end{itemize}

\cvtag{EC2}
\cvtag{EFS}
\cvtag{EKS}
\cvtag{IAM}
\cvtag{S3}
\cvtag{SNS}
\cvtag{SQS}
\cvtag{VPC}
\cvtag{OpenSearch Service}
\cvtag{Route53}
\cvtag{Lambda}
\cvtag{CloudFormation}



\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip


\clearpage
